---
title: "prepareGLYCIM"
author: "Chuchung Chen"
date: "October 26, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r create}
library(magrittr)
#s <- 1  # numbers of simulation
fname <- {}
sname <- {}
counter <- 1
  
create <- readxl::read_excel("R Interface/Int.xlsx","int") # use excel
#create <- read.table("R Interface/Int.csv",sep=",",header=TRUE)
Var <- read.table("R Interface/Variety.csv",sep=",",header=TRUE)

# 2:8  9:15  16:21  22:26
for(s in (2:8)){

  Description.no <- s # the rank of simulation

  name.folder <- as.character(create$name_of_folder[s])
  
  name.wea <- as.character(create$Weather_ID[s])
  name.stdwea <- as.character(create$STD_weather_ID[s])
  name.soil <- as.character(create$Soil_ID[s])
  name.int <- name.folder
  name.var <- as.character(create$Variety[s])
  name.water <- as.character(name.folder)
  y <- as.character(create$Year[s])

  dir.create(name.folder) # create folder
  create1 <- create[s,] 
  
  write.int(create1)
  write.water(create1)
  read.table(paste0("Weather/",name.wea,".csv"),sep=",",header=TRUE)  %>% wea2GLYCIM %>% 
  write.wea(paste0(name.folder,"/",name.wea),.)
  write.run(create1)

  write.var(Var)
  fname[counter] <- name.folder
  sname[counter] <- name.soil
  counter = counter + 1 

  sink() # end the sink, to avoid sink stack is full
  gc()
}
  write.bat(fname,sname)

```


```{r bat}
write.bat <- function(id,soil){

  sink("copy.bat")
  for(i in 1:(length(id))){

    
     cat("copy"," " )
     cat('"')
     cat("R Interface\\GLYCIM.exe")
     cat('"')
     cat("  ")
     cat(id[i],"\n")

     cat("copy"," " )
     cat('"')
     cat("R Interface\\Glycim_090821.exe")
     cat('"')
     cat("  ")
     cat(id[i],"\n")
     
     
     cat("copy"," " )
     cat('"')
     cat("R Interface\\Soil\\")
     cat(paste0(soil[i],".soi"))
     cat('"')
     cat("  ")
     cat(id[i],"\n")

     
     cat("copy"," " )
     cat("Weather\\")
     cat(paste0(name.stdwea,".wea"))
     cat("  ")
     cat(id[i],"\n")

  }
  sink()
  
    sink("runGLYCIM.bat")
    cat(paste0('for /R ','"', 'D:\\GLYCIM_2021\\GLYCIM\\' ,'"',' %%g in (.) do (', '\n'))
    cat("pushd %%g","\n")
    cat("echo now in %%g","\n")
    cat("Glycim.exe ","\n")    
    cat("popd","\n")
    cat(")")
    cat("pause")
  sink()
  
}

gc()
```



## make run
```{r run, echo=FALSE}
write.run <- function(df){
  sink(paste0(name.folder,"/","Run.dat"))
  cat(paste0(name.wea,".WEA"),"\n")
  cat(paste0(name.stdwea,".WEA"),"\n")
  cat(paste0(name.soil,".SOI"),"\n")
  cat(paste0(name.int,".INt"),"\n")
  cat(paste0(name.var,".VAR"),"\n")
  cat(paste0(name.water,".DAT"),"\n")
  cat(paste0(name.folder,".g01"),"\n")
  cat(paste0(name.folder,".out"),"\n")
  cat(paste0(name.folder,".sum"),"\n")
  cat(paste0(name.folder,".tab"),"\n")
  
  sink()
  
}

#write.run(create)

```



## make int
```{r int, echo=FALSE}
# directly use the create dataframe


write.int <- function(df){
  df <- create1
  
  date0 <- as.Date(paste(df$Year,01,01,sep="/"),"%Y/%m/%d")
  date1 <- as.Date(df$Sowing,"%Y/%m/%d")
  date2 <- as.Date(df$Harvest,"%Y/%m/%s")
  
  sink(paste0(name.folder,"/",name.int,".INT"))
    # line 1
    cat(df$Latitude,date1-date0+1+3,date2-date0+1," ")
    cat(specify_decimal(as.numeric(df$RowSpace)*0.3937,2), specify_decimal(30.48/as.numeric(df$PlantSpace),2), " ")
    cat(df$RowAngle,df$ReportFreq,df$Hour,df$CO2,"\n")

    # line 2    
    cat(specify_decimal(as.numeric(df$NO3_N)*2*0.8922,2), specify_decimal(as.numeric(df$NH4_N)*2*0.8922,2)," ")
    cat(specify_decimal(as.numeric(df$Napplied)*0.8922,1)," ")
    cat(df$NO3inN,df$NH4inN, specify_decimal(as.numeric(df$OrganicMatter)*2*0.8922,2),"\n")
    # line 3 
    cat(df$CellNumberVertical,df$CellNumberRow,df$CellDepth,df$depth_of_cultivated," ")
    cat(df$depth_gas_impermeable,df$T_of_soil_lower_boundary,"0","\n")
    cat(6,2, "\n")
    cat("    ", 0.0021, 0.0018,"\n")  #1
    cat("    ", 0.0015, 0.0012,"\n")  
    cat("    ", 0.0011, 0.0010,"\n")  #3
    cat("    ", 0.0011, 0.0010,"\n")
    cat("    ", 0.0006, 0.0003,"\n")  #5
    cat("    ", 0.0006, 0.0003,"\n")
    #cat("    ", 0.012, 0.011, 0.005,"\n")  #7
    #cat("    ", 0.012, 0.011, 0.005,"\n")
    #cat("    ", 0.012, 0.011, 0.005,"\n")  #9
    #cat("    ", 0.012, 0.011, 0.005,"\n")
  sink()
}


write.water <- function(df){
  sink(paste0(name.folder,"/",name.water,".dat"))
    cat("Furrow","\n")

    cat(df$Times_of_Irrigation,"\n")
    
    if(df$Times_of_Irrigation>=1){
      
      for(w in 1:df$Times_of_Irrigation){
        item <- paste0("Date",w,"_Irrigation")
        Date <- subset(df,select=item)[[1]]
      
        item <- paste0("Amount",w)
        depth <- subset(df,select=item)[[1]] * 0.394
        depth <- round(depth,3)
      
        cat(format(Date,format="%m/%d/%y"),"\t",round(depth,3),"\n")
      }
    }
   
    

   sink()
}

```

## make var
```{r var,echo=FALSE}
Var <- read.table("R Interface/Variety.csv",sep=",",header=TRUE)

specify_decimal <- function(x, k) trimws(format(round(x, k), nsmall=k))

write.var <- function(df){
  vname <- name.var
  var <-  subset(df, select=c("Abbr",vname))
   var<- var[,2]
  
  sink(paste0(name.folder,"/",vname,".VAR"))
    
    cat(" ",var[2]," ",var[3]," ",var[4]," ",var[5],"\n")
    cat("  "," ",specify_decimal(var[6],6),  1, "\n")
    cat( "  "," ",specify_decimal(var[7],6), 2, "\n")
    cat("  "," ",specify_decimal(var[8],6),  3, "\n")
    cat("  "," ",specify_decimal(var[9],6),  4, "\n")
    cat("  "," ",specify_decimal(var[10],6),  5, "\n")
    cat("  "," ",specify_decimal(var[11],6),  6, "\n")
    cat("  "," ",specify_decimal(var[12],6),  7, "\n")
    cat("  "," ",specify_decimal(var[13],6),  8, "\n")
    cat("  "," ",specify_decimal(var[14],6),  9, "\n")
    cat("  ","",specify_decimal(var[15],6),  10, "\n")
    cat("  "," ",specify_decimal(var[16],6),  11, "\n")
    cat("  ",specify_decimal(var[17],6),  12, "\n")
    cat("  ",specify_decimal(var[18],6),  13, "\n")
    cat("  "," ",specify_decimal(var[19],6),  14, "\n")
    cat("  "," ",specify_decimal(var[20],6),  15, "\n")
    cat("  "," ",specify_decimal(var[21],6),  16, "\n")
    cat("  "," ",specify_decimal(var[22],6),  17, "\n")
    cat("  "," ",specify_decimal(var[23],6),  18, "\n")
    cat("  "," ",specify_decimal(var[24],6),  19, "\n")
    cat("  "," ",specify_decimal(var[25],6),  20, "\n")
    cat("  "," ",specify_decimal(var[26],6),  21, "\n")
    cat("  "," ",specify_decimal(var[27],6),  22, "\n")
    cat("  "," ",specify_decimal(var[28],6),  23, "\n")
    cat("  "," ",specify_decimal(var[29],6),  24, "\n")
    cat("  "," ",specify_decimal(var[30],6),  25, "\n")
  
  sink()
}




```


## make wea


### to GLYCIM
THE following chrunk making the weather file for GLYCIM model, two functions were made here. 
The *wea2GLYCIM* function directly extrat the values according to column names, therefore, it is  
important to check the columnname here. The *write.wea* function make wea file for GLYCIM model.<br>
*The format of wea for GLYCIM were as follows*

|JDAY         |DATE                      | TMAX     | TMIN     |  RAIN    |  WIND          |
|-------------|--------------------------|----------|----------|----------|----------------|
|day of year  |characters denoting date  |max air T |min air T |rainfall  |wind run at 2 m |
|Julian date  |'mm/dd'                   |o F       |o F       |inch/day  |miles/day       |

Numbers and characters are written in free format <br/>
1 MJ/m2 = 23.900574 langley <br/>
1  mm = 0.03937 inch  <br/>
1 m/s = 53.69 miles/day <br/>
T(f) = T(c) * 1.8 +32 <br/>

```{r func wea, echo=FALSE}

# change weather format to GLYCIM
wea2GLYCIM <- function(df){
  
  date0 <- as.Date(paste(y,01,01,sep="/"),"%Y/%m/%d")
  date <- as.Date(paste(y,df$Month,df$Day,sep="/"),"%Y/%m/%d")
  Jday <- NA
  for(d in 1:nrow(df)){ Jday[d] <- date[d] - date0 + 1   }
  
  MONTH <- df$Month
  DAY <- df$Day
  SolRad <- df$SolRad * 23.9
  Tmax <- df$Tmax * 1.8 + 32
  Tmin <- df$Tmin * 1.8 + 32 
  RAIN <- df$Precp * 0.03937
  WIND <- df$WS * 53.69
  
  GLYCIM.df <- data.frame(Jday, MONTH, DAY, SolRad, Tmax, Tmin, RAIN , WIND)
  
  return(GLYCIM.df)
}

# write wea file for GLYCIM
write.wea <- function(fname,df){
  sink(paste0(fname,".wea"))
  
  cat("'",fname,"'","\n")
  for(i in 1:nrow(df)){
    cat(df[i,1]," ")
    cat("'")
    m.glycim <- if(df[i,2]>9){df[i,2]}else{paste0("0",df[i,2])}
    cat(m.glycim)
    cat("/")
    d.glycim <- if(df[i,3]>9){df[i,3]}else{paste0("0",df[i,3])}
    cat(d.glycim)
    cat("'")
    cat(" ")
    cat(specify_decimal(df[i,4],2),"\t", specify_decimal(df[i,5],2),"\t")
    cat(specify_decimal(df[i,6],2),"\t",specify_decimal(df[i,7],2),"\t",specify_decimal(df[i,8],2))
    cat("\n")
  }
 sink() 
}
```

### read/write wea
This chunk reads the weather file and write into the wea for GYLCIM.
```{r GLYCIM wea,warning=FALSE }
library(magrittr)

y = 2018 # this is important here, the wea2GLYCIM share the global variant "y"

read.table(paste0("Weather/",name.wea,".csv"),sep=",",header=TRUE)  %>% wea2GLYCIM  %>% 
write.wea(paste0(name.folder,"/",name.wea),.)

 df <- read.table(paste0("Weather/KDARES_10",".csv"),sep=",",header=TRUE)  
 df1 <- wea2GLYCIM(df)
 
write.wea(paste0("weather/","KDARES_GLYCIM.wea"),df1)


# rm(MONTH, Month, month.vcsvname,Tmax,Tmin,date,date0)

```
